### 2013-05-30 inst/examples/BUGS/process-noise-only.Rmd
still debugging data formatting

```{r plotting-options, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE}
setwd("~/Documents/code/nonparametric-bayes/inst/examples/BUGS/")
#library(knitcitations)
library(ggplot2) 
library(nonparametricbayes) 
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=TRUE, comment=NA,
               fig.width=6, fig.height=4, cache.path="process/", verbose=TRUE)
#opts_knit$set(upload.fun = socialR::flickr.url)
theme_set(theme_bw(base_size=12))
theme_update(panel.background = element_rect(fill = "transparent", colour = NA),
             plot.background = element_rect(fill = "transparent", colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
               "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r}
require(modeest)
posterior.mode <- function(x) {
 # ux <- unique(x)
 #  ux[which.max(tabulate(match(x, ux)))]
 mlv(x, method="shorth")$M
}

@@

```{r allen-output, dependson="allen-traces"}
# A <- allen_posteriors
# A$index <- A$index + A$chain * max(A$index) # Combine samples across chains by renumbering index 
# pardist <- acast(A[-4], index ~ variable, subset=.(variable != "deviance") )
pardist <- acast(allen_posteriors[2:3], 1:table(allen_posteriors$variable)[1] ~ variable) 
pardist[,"logr0"] = exp(pardist[,"logr0"]) # transform model parameters back first
pardist[,"logtheta"] = exp(pardist[,"logtheta"])

@@

```{r ricker-output, dependson="ricker-traces"}
ricker_pardist <- acast(ricker_posteriors[2:3], 
                        1:table(ricker_posteriors$variable) ~ variable, 
                        subset=.(variable!="deviance")) 
ricker_pardist[,"logr0"] = exp(ricker_pardist[,"logr0"]) # transform model parameters back first
bayes_coef <- apply(ricker_pardist,2, posterior.mode) # much better estimates from mode then mean
ricker_bayes_pars <- unname(c(bayes_coef[2], bayes_coef[1]))
ricker_means <- sapply(x_grid, Ricker, 0, ricker_bayes_pars[c(1,2)])
```

@@

```{r myers-mcmc, dependson="myers-model"}
jags.params=c("logr0", "logtheta", "logK", "stdQ")
jags.inits <- function(){
  list("logr0"=log(rlnorm(1,0,.1)), 
       "logK"=log(7 * rlnorm(1,0,.1)),
       "logtheta" = log(2 * rlnorm(1,0,.1)),  
       "stdQ"=sqrt(0.5) * rlnorm(1,0,.1),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
myers_jags <- do.call(jags, 
                      list(data=jags.data, inits=jags.inits, jags.params, 
                           n.chains=n.chains, n.iter=n.iter, n.thin=n.thin,
                           n.burnin=n.burnin, model.file="myers_process.bugs"))
myers_jags <- do.call(autojags, 
                      list(myers_jags, n.update=10, n.iter=n.iter, 
                           n.thin = n.thin, progress.bar="none"))
```

@@

```{r myers-output, dependson="myers-traces"}
myers_pardist <- acast(myers_posteriors[2:3], 
                        1:table(myers_posteriors$variable) ~ variable, 
                        subset=.(variable!="deviance")) 
myers_pardist[,1] = exp(myers_pardist[,1]) # transform model parameters back first
myers_pardist[,2] = exp(myers_pardist[,2]) # transform model parameters back first
myers_pardist[,3] = exp(myers_pardist[,3]) # transform model parameters back first
colnames(myers_pardist) = c("K", "r0", "theta", "stdQ")
bayes_coef <- apply(myers_pardist,2, posterior.mode) # much better estimates
myers_bayes_pars <- unname(c(bayes_coef[2], bayes_coef[3], bayes_coef[1]))
myers_means <- sapply(x_grid, Myer_harvest, 0, myers_bayes_pars)
```

@@

```{r}
df <- acast(allen_posteriors[2:3], 1:table(allen_posteriors$variable) ~ variable) 
modes <- apply(df, 2, posterior.mode)
allen_deviance <- modes[['deviance']]

>>>>

```{r plotting-options, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE}
source("~/.knitr_defaults.R")
#opts_knit$set(upload.fun = socialR::flickr.url)
library(knitcitations)
library(nonparametricbayes) 
```

```{r posterior-mode}
require(modeest)
posterior.mode <- function(x) {
 mlv(x, method="shorth")$M
}

@@

```{r allen-output, dependson=c("posterior-mode", "allen-traces")}
# A <- allen_posteriors
# A$index <- A$index + A$chain * max(A$index) # Combine samples across chains by renumbering index 
# pardist <- acast(A[-4], index ~ variable, subset=.(variable != "deviance") )
pardist <- acast(allen_posteriors[2:3], 1:table(allen_posteriors$variable)[1] ~ variable) 
pardist[,"logr0"] = exp(pardist[,"logr0"]) # transform model parameters back first
pardist[,"logtheta"] = exp(pardist[,"logtheta"])

@@

```{r ricker-output, dependson=c("posterior-mode", "ricker-traces")}
ricker_pardist <- acast(ricker_posteriors[2:3], 
                        1:table(ricker_posteriors$variable) ~ variable, 
                        subset=.(variable!="deviance")) 
ricker_pardist[,"logr0"] = exp(ricker_pardist[,"logr0"]) # transform model parameters back first
bayes_coef <- apply(ricker_pardist,2, posterior.mode) # much better estimates from mode then mean
ricker_bayes_pars <- unname(c(bayes_coef[2], bayes_coef[1]))
ricker_means <- sapply(x_grid, Ricker, 0, ricker_bayes_pars[c(1,2)])
```

@@

```{r myers-mcmc, dependson="myers-model"}
jags.params=c("logr0", "logtheta", "logK", "stdQ")
jags.inits <- function(){
  list("logr0"=log(rlnorm(1,0,.1)), 
       "logK"=log(7 * rlnorm(1,0,.1)),
       "logtheta" = log(2 * rlnorm(1,0,.1)),  
       "stdQ"=sqrt(0.5) * rlnorm(1,0,.1),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
myers_jags <- do.call(jags, 
                      list(data=jags.data, inits=jags.inits, jags.params, 
                           n.chains=n.chains, n.iter=n.iter, n.thin=n.thin,
                           n.burnin=n.burnin, model.file="myers_process.bugs"))
recompile(myers_jags)
myers_jags <- do.call(autojags, 
                      list(myers_jags, n.update=10, n.iter=n.iter, 
                           n.thin = n.thin, progress.bar="none"))
```

@@

```{r myers-output, dependson=c("posterior-mode", "myers-traces")}
myers_pardist <- acast(myers_posteriors[2:3], 
                        1:table(myers_posteriors$variable) ~ variable, 
                        subset=.(variable!="deviance")) 
myers_pardist[,1] = exp(myers_pardist[,"logK"]) # transform model parameters back first
myers_pardist[,2] = exp(myers_pardist[,"logr0"]) # transform model parameters back first
myers_pardist[,3] = exp(myers_pardist[,"logtheta"]) # transform model parameters back first
colnames(myers_pardist) = c("K", "r0", "theta", "stdQ")
bayes_coef <- apply(myers_pardist,2, posterior.mode) # much better estimates
myers_bayes_pars <- unname(c(bayes_coef[2], bayes_coef[3], bayes_coef[1]))
myers_means <- sapply(x_grid, Myer_harvest, 0, myers_bayes_pars)
```

@@

```{r, dependson=("posterior-mode","myers-output", "ricker-output", "allen-output", "gp-output", "mle-output") }
df <- acast(allen_posteriors[2:3], 1:table(allen_posteriors$variable) ~ variable) 
modes <- apply(df, 2, posterior.mode)
allen_deviance <- modes[['deviance']]
